\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-09-13 manuscript.Rmd

```{r dependencymanager, include = FALSE}
library(packrat)
packrat::init()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)

>>>>

```{r dependencymanager, include = FALSE, warning=F}
knitr::opts_chunk$set(warning = F, error = F, message = F)
library(packrat)
packrat::init()
#Only use when you have added some pack
#packrat::snapshot(ignore.stale=TRUE)
